\textbf{EECS 340: Assignment 3}

### 2020-02-20 assignment_3/article.tex
💄 Polish Question 1(d) math expression.

\section{(d) $T(n) = aT(\frac{n}{a}) + \Theta(n^{\lambda}(\log n)^b)$}
For this recurrance, we have a comparsion between $n^{\log_a a}$ and $n^{\lambda}(\log n)^b)$, which is equivalent to comparing $n$ and $n^{\lambda}(\log n)^b)$. We may prove that $n$ is polynomially larger than $n^{\lambda}(\log n)^b)$ by analyzing:

>>>>

\section{(d) $T(n) = aT(\frac{n}{a}) + \Theta(n^{\lambda}(\log n)^b)$}
For this recurrance, we have a comparsion between $n^{\log_a a}$ and $n^{\lambda}(\log n)^b$, which is equivalent to comparing $n$ and $n^{\lambda}(\log n)^b$. We may prove that $n$ is polynomially larger than $n^{\lambda}(\log n)^b$ by analyzing:
